full title

### 2020-11-20 paper/pldi21/ds.tex
ds.tex

To prove the termination of the abstract interpretation with the combined
domain, the condition provides an upper bound of the number of sealed symbolic
states after the sensitive abstract states are reached the fixed point.  Thus,
the termination of the analysis is guaranteed.  For the proof of Soundness, two
properties (\ref{equ:sound-join}) for join operator $\join$ and
(\ref{equ:sound-step}) for combined one-step execution are required to be
proved.  The core idea of the proof is to prove the following lemmas for
$\triage$ function and utilize them.
\begin{lemma}\label{lemma:step-symb}
  Assume that the following condition is hold
  \[
    \forall (\absimap, \symbst) \in \symbelem. \; \exists \symbst' \in
    \symbstset. \; \text{s.t.} \; \symbst \symbtrans \symbst'
  \]
  then the following property holds:
  \[
    \step \circ \symbgamma(\symbelem) \subseteq
    \symbgamma \circ \symbstep(\symbelem)\\
  \]
\end{lemma}
\begin{lemma}\label{lemma:triage}
  For a given combined state $\combelem \in \combdom$, the $\triage$ function
  satisfies the following two properties:
  \begin{itemize}
    \item $\combgamma(\combelem) \subseteq \combgamma \circ \triage(\combelem)$
    \item $\forall (\absimap, \symbst) \in \symbelem. \; \exists \symbst' \in
      \symbstset.  \; \text{s.t.} \; \symbst \symbtrans \symbst'$
  \end{itemize}
  where $(\sabselem, \symbelem) = \triage(\combelem)$
\end{lemma}

>>>>

To prove the termination of the abstract interpretation with the combined
domain, the condition provides an upper bound of the number of sealed symbolic
states after the sensitive abstract states are reached the fixed point.  Thus,
the termination of the analysis is guaranteed.  For the proof of Soundness, two
properties (\ref{equ:sound-join}) for join operator $\join$ and
(\ref{equ:sound-step}) for combined one-step execution are required to be
proved.  The core idea of the proof is to use Lemma~\ref{lemma:step-symb} and
Lemma~\ref{ref:lemma:trage} for the sealed symbolic one-step execution
$\symbstep$ and the $\triage$ function. Because of the page limitation, we omit
the proof in this paper and include it in a companion report~\cite{report}.
\begin{lemma}\label{lemma:step-symb}
  Assume that the following condition is hold
  \[
    \forall (\absimap, \symbst) \in \symbelem. \; \exists \symbst' \in
    \symbstset. \; \text{s.t.} \; \symbst \symbtrans \symbst'
  \]
  then the following property holds:
  \[
    \step \circ \symbgamma(\symbelem) \subseteq
    \symbgamma \circ \symbstep(\symbelem)\\
  \]
\end{lemma}
\begin{lemma}\label{lemma:triage}
  For a given combined state $\combelem \in \combdom$, the $\triage$ function
  satisfies the following two properties:
  \begin{itemize}
    \item $\combgamma(\combelem) \subseteq \combgamma \circ \triage(\combelem)$
    \item $\forall (\absimap, \symbst) \in \symbelem. \; \exists \symbst' \in
      \symbstset.  \; \text{s.t.} \; \symbst \symbtrans \symbst'$
  \end{itemize}
  where $(\sabselem, \symbelem) = \triage(\combelem)$
\end{lemma}
